---
title: "Telco Customer Churn"
author: "Pradeep Rai"
date: "October 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Customer churn, also known as customer attrition, customer turnover, or customer defection, is the loss of clients or customers.

Banks, telephone service companies, Internet service providers, pay TV companies, insurance firms, and alarm monitoring services, often use customer attrition analysis and customer attrition rates as one of their key business metrics (along with cash flow, EBITDA, etc.) because the cost of retaining an existing customer is far less than acquiring a new one.[1] Companies from these sectors often have customer service branches which attempt to win back defecting clients, because recovered long-term customers can be worth much more to a company than newly recruited clients

## Data

The data will be aquired from dataset [Telco Customer Churn](https://www.kaggle.com/pavanraj159/telecom-customer-churn-prediction/notebook) available on Kaggle.com
Each row represents a customer, each column contains customer’s attributes described on the column Metadata.
The raw data contains 7043 rows (customers) and 21 columns (features). The “Churn” column is our target.

## Data Modeling:

In brief, outline your approach to solving this problem (knowing that this might change later).

## Deliverables:

1. Code
    +  Read dataset/ Exploratory Data Analysis (EDA)
    +  Pre-processing
      -  Train/Test Splits + Build Initial Model
      -  Model Tuning + Evaluation
      -  Reporting

2. Capstone Project Report



When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
